Empirical Bayes analysis for detection of gene heterosis in RNAseq data

### 2014-12-17 ebayes_rnaseq_heterosis.tex
include placeholder real data figs

@@

>>>>

\subsection{RNAseq experiment to identify genes demonstrating heterosis}
\label{s:experiment}

@@

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{maize_volcano}}
\caption{A two-dimensional histogram of the probability of heterosis versus effect size, $\mu_{g3}-\max(\mu_{g1},\mu_{g3})$ if $P(HPH|y)>P(LPH|y)$ or $\mu_{g3}-\min(\mu_{g1},\mu_{g2})$ if $P(HPH|y)<P(LPH|y)$ for the B73 $\times$ Mo17 maize experiment.}
\label{f:volcano}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{normality}}
\caption{One and two-dimensional histograms for gene-specific parameters from a single MCMC iteration, $\theta_g^{(m)}$,  for the B73 $\times$ Mo17 maize experiment. For reference, the one dimensional histograms have the marginal probability density functions from $N(\hat{\eta},\hat{\Sigma})$.}
\label{f:normality}
\end{figure}
